---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Conor Lacey"
date: "03/21/2023"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
suppressWarnings(library(tidyverse))
suppressWarnings(library(tidymodels))
suppressWarnings(library(openintro))
```

### Exercise 1

```{r m_bty}
m_bty <- lm(evals$score~evals$bty_avg)
summary(m_bty)
```

The linear model is: 

score = 3.88 + 0.07(bty_avg)

The R^2 value is: 

0.035

The Adjusted R^2 is: 

0.033

### Exercise 2

```{r m_bty_gen}
m_bty_gen <- lm(evals$score~evals$bty_avg+evals$gender)
summary(m_bty_gen)
```

The linear model is: 

score = 3.74 + 0.07(bty_avg) + 0.17(gender)

The R^2 value is: 

0.06

The Adjusted R^2 is: 

0.06

### Exercise 3

Looking at m_bty_gen, we can notice a few things. The intercept indicates the predicted average evaluation score of female professors with an average beauty rating of 0. The bty_avg slope indicates that for every 1 point increase in bty_avg a professor's estimated average evaluation score increases by 0.07. The gender slope indicates that if a professor is a male, their predicted average evaluation score will increase by 0.17. 


### Exericse 4

5.9% iof the variability in score can be explained by the m_bty_gen model.

### Exercise 5

score = 3.91 + 0.07(bty_avg)

### Exercise 6

Male

### Exercise 7

```{r male and female score~bty_avg}
evals %>% ggplot (aes(x = bty_avg, y = score, color = gender)) + 
  geom_smooth(method = lm, se = FALSE, fullrange = TRUE)
```


Males typically have a stronger relationship between bty_avg and scores than females.

### Exercise 8 

The adjusted R^2 value for m_bty is smaller than m_bty_gen. The gender variable helps by explaining more variance in the scores when we already have information on the beauty score of the professor. 

### Exercise 9

The addition of gender didn't really change the bty_avg slope between m_bty and m_bty_gen.

### Exercise 10





