---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Conor Lacey"
date: "03/21/2023"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
suppressWarnings(library(tidyverse))
suppressWarnings(library(tidymodels))
suppressWarnings(library(openintro))
```

### Exercise 1

```{r m_bty}
m_bty <- lm(evals$score~evals$bty_avg)
summary(m_bty)
```

The linear model is: 

score = 3.88 + 0.07(bty_avg)

The R^2 value is: 

0.035

The Adjusted R^2 is: 

0.033

### Exercise 2

```{r m_bty_gen}
m_bty_gen <- lm(evals$score~evals$bty_avg+evals$gender)
summary(m_bty_gen)
```

The linear model is: 

score = 3.74 + 0.07(bty_avg) + 0.17(gender)

The R^2 value is: 

0.06

The Adjusted R^2 is: 

0.06

### Exercise 3

Looking at m_bty_gen, we can notice a few things. The intercept indicates the predicted average evaluation score of female professors with an average beauty rating of 0. The bty_avg slope indicates that for every 1 point increase in bty_avg a professor's estimated average evaluation score increases by 0.07. The gender slope indicates that if a professor is a male, their predicted average evaluation score will increase by 0.17. 


### Exericse 4

5.9% iof the variability in score can be explained by the m_bty_gen model.

### Exercise 5

score = 3.91 + 0.07(bty_avg)

### Exercise 6

Male

### Exercise 7

```{r male and female score~bty_avg}
evals %>% ggplot (aes(x = bty_avg, y = score, color = gender)) + 
  geom_smooth(method = lm, se = FALSE, fullrange = TRUE)
```


Males typically have a stronger relationship between bty_avg and scores than females.

### Exercise 8 

The adjusted R^2 value for m_bty is smaller than m_bty_gen. The gender variable helps by explaining more variance in the scores when we already have information on the beauty score of the professor. 

### Exercise 9

The addition of gender didn't really change the bty_avg slope between m_bty and m_bty_gen.

### Exercise 10

```{r m_bty_rank}
m_bty_rank <- lm(evals$score ~ evals$gender + evals$rank)
summary(m_bty_rank)
```

The linear model is: 

score = 4.2 + .17(gender) + -0.1(tenure_tack) + -.17(tenured)

Looking at m_bty_rank, we can notice a few things. The intercept indicates the predicted average evaluation score of female teaching professors. The gender slope indicates professor's average evaluation score increases by .17 if they are male. The tenure_track slope indicates that tenure_track professors decrease in their predicted average evaluation score by -.1. The tenured slope indicates that tenured professors decrease in their predicated average evaluation score by -.17.

### Exercise 11

Total number of students in the class. I can't think of any reason why number of students would be related to evaluation scores.

### Exercise 12

```{r m_cls_students}
m_cls_students <- lm(evals$score ~ evals$cls_students)
summary(m_cls_students)
```

Haha! I was right. 

### Exercise 13 

cls_perc_eval should not be included. cls_did_eval is essentially the same variable except it is not in percent form, it is instead a count of students who completed the evaluation. However, using a count versus using a percent seems arbitrary for linear models considering they are both describing the magnitude of students who completed the evaluation. As a result, I think we can take this one out because it would be doing the same thing as cls_did_eval.

### Exercise 14

```{r m_allvars}
attach(evals)
m_allvars <- lm(score ~ rank + ethnicity + gender + language + age +cls_did_eval +
                  cls_students + cls_level + cls_profs + cls_credits + bty_avg) 
summary(m_allvars)
detach(evals)
```

### Exercise 15 

```{r backwards selection}
attach(evals)
m_allvars <- lm(score ~ ethnicity + gender + language + age + cls_did_eval +
                  cls_students + cls_credits + bty_avg) 
summary(m_allvars)
detach(evals)
```

The linear model is: 

score = 3.83 + non_minority(.17) + male(.19) + non-English(-.17) + age(-.005) + cls_did_eval(0.007) + cls_students(-0.004) + credit(0.54) + bty_avg(0.066)

